---
title: "clamour"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{clamour}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

_clamour_ is a package to help with building a website to display the results
of analysis of Twitter hashtags, usually associated with an event such as an
academic conference. The package provides some basic infrastructure and examples
to help you get set up.

```{r library}
library(clamour)
```

This vignette will take you through the basics of setting up a _clamour_
project, analysis of an example dataset and how to host the results on a website
using [GitHub pages][pages].

# Setting up

To start a _clamour_ project we can use the `clamour_setup` function. This will
create a basic directory structure with some template files. We just need to
provide the function with a path to the new project directory. For this vignette
we use a temporary directory.

```{r setup}
path <- fs::path(tempdir(), "example")
clamour_setup(path)
```

The result is the following directory structure:

```{r directory}
fs::dir_tree(path)
```

* `analysis/` - Analysis files for each hashtag
* `data/` - Data files containing tweets
* `docs/` - The rendered website files

[pages]: https://pages.github.com/ "GitHub pages"
