```{r analysis-setup}
# Convert days to dates
start_date <- as_date(params$start_day)
end_date <- as_date(params$end_day)
days <- seq(start_date, end_date, by = 1)

# Set random seed
set.seed(params$seed)

# Set ggplot2 theme
theme_set(match.fun(params$theme)())
theme_update(
    axis.text        = element_text(size = 12),
    axis.title       = element_text(size = 12),
    legend.position  = "bottom",
    strip.background = element_rect(fill = params$accent)
)

# Tweet type scales
scale_fill_tweet_type = scale_fill_manual(
    name   = "Tweet type",
    limits = c(TRUE, FALSE),
    labels = c("Original", "Retweet"),
    values = c(params$accent, params$accent2)
)
scale_colour_tweet_type = scale_colour_manual(
    name   = "Tweet type",
    limits = c(TRUE, FALSE),
    labels = c("Original", "Retweet"),
    values = c(params$accent, params$accent2)
)
```

```{r query-hashtags, eval = length(hashtags_vec) > 1}
asis_output("## Query hashtags\n")

plot_data <- map_dfr(hashtags_vec, function(.hashtag) {
    tweets %>%
        filter(str_detect(tolower(text), tolower(.hashtag))) %>%
        group_by(is_retweet) %>%
        summarise(Count = n()) %>%
        mutate(Hashtag = .hashtag)
})

ggplot(plot_data, aes(x = Hashtag, y = Count, fill = !is_retweet)) +
    geom_col() +
    scale_fill_tweet_type +
    labs(title = "Number of tweets for each query hashtag")
```

# Timeline

## Tweets by day

```{r tweets-by-day}
tweets %>% 
    group_by(date, is_retweet) %>%
    summarise(count = n()) %>%
    ggplot(aes(date, count, fill = !is_retweet)) +
    geom_col() +
    scale_fill_tweet_type +  
    labs(x = "Date", y = "Tweets",
         title = paste(hashtags_query, "tweets per day"))
```

## Tweets by day and time

Filtered for dates `r params$start_day` - `r params$end_day` in the
`r params$timezone` timezone.

```{r tweets-by-day-hour, eval = Sys.Date() >= start_date}
tweets_days <- tweets %>% 
    filter(date >= start_date, date <= end_date) %>%
    group_by(date, hour)

tweets_days %>%
    group_by(date, hour, is_retweet) %>%
    summarise(count = n()) %>% 
    ggplot(aes(hour, count, fill = !is_retweet)) +
        geom_col() +
        scale_fill_tweet_type +
        facet_grid(strftime(date, "%b %d") ~ .) + 
        labs(x = "Hour", y = "Tweets",
             title = paste(hashtags_query, "tweets by time of day"),
             subtitle = paste("tweets between", params$start_day, "and",
                              params$end_day))
```

# Users

## Top tweeters {.tabset .tabset-pills}

### Overall {.unnumbered}

```{r tweets-top-users}
tweets %>%
    group_by(screen_name, is_retweet) %>%
    summarise(count = n()) %>%
    group_by(screen_name) %>%
    mutate(total = sum(count)) %>%
    ungroup() %>%
    arrange(desc(total)) %>%
    slice(1:20) %>% 
    ggplot(aes(reorder(screen_name, total), count, fill = !is_retweet)) +
        geom_col() +
        scale_fill_tweet_type +
        coord_flip() + 
        labs(x = "Screen Name", y = "Tweets",
             title = paste(hashtags_query, "tweets by user"),
             subtitle = "top 20 users")
```

### Original {.unnumbered}

```{r tweets-top-users-orig}
tweets %>%
    filter(is_retweet == FALSE) %>%
    count(screen_name) %>% 
    arrange(desc(n)) %>%
    slice(1:20) %>% 
    ggplot(aes(reorder(screen_name, n), n)) +
        geom_col(fill = params$accent) +
        coord_flip() + 
        labs(x = "Screen Name", y = "Tweets",
             title = paste(hashtags_query, "tweets by user"),
             subtitle = "top 20 users (original)")
```

### Retweets {.unnumbered}

```{r tweets-top-users-retweet}
tweets %>%
    filter(is_retweet == TRUE) %>%
    count(screen_name) %>% 
    arrange(desc(n)) %>%
    slice(1:20) %>% 
    ggplot(aes(reorder(screen_name, n), n)) +
        geom_col(fill = params$accent2) +
        coord_flip() + 
        labs(x = "Screen Name", y = "Tweets",
             title = paste(hashtags_query, "tweets by user"),
             subtitle = "top 20 users (retweets)")
```

## Retweet proportion

```{r tweets-retweet-prop}
plot_data <- tweets %>%
    group_by(screen_name) %>%
    summarise(orig = sum(!is_retweet),
              retweet = sum(is_retweet)) %>%
    mutate(total = orig + retweet)

ggplot(plot_data, aes(total, (orig / total) - (retweet / total))) +
    geom_hline(yintercept = 0, colour = "red") +
    geom_point(colour = params$accent) +
    geom_text_repel(data = top_n(plot_data, 10, total), 
                    aes(label = screen_name)) +
    labs(x = "Total tweets",
         y = "<<< more retweets : more original tweets >>>",
         title = paste(hashtags_query, "original tweets compared to retweets"),
         subtitle = "top 10 users labelled")
```

## Top tweeters timeline

```{r tweets-top-users-time}
top_users <- tweets %>%
    count(screen_name) %>% 
    arrange(desc(n)) %>%
    slice(1:5) %>%
    pull(screen_name) %>%
    fct_inorder()

tweets %>%
    filter(screen_name %in% top_users) %>%
    mutate(screen_name = factor(screen_name,
                                levels = levels(top_users))) %>%
    ggplot(aes(datetime, 1, colour = !is_retweet)) +
        geom_jitter(width = 0, height = 1) +
        scale_colour_tweet_type +
        facet_wrap(~ screen_name, ncol = 1) +
        labs(x = "Datetime",
             title = paste(hashtags_query, "top users timeline"),
             subtitle = "when the top 5 users tweeted") + 
        theme(axis.title.y = element_blank(),
              axis.text.y = element_blank(),
              axis.ticks.y = element_blank(),
              legend.position = "bottom")
```

## Top tweeters by day {.tabset .tabset-pills}

### Overall {.unnumbered .tabset .tabset-fade}

```{r tweets-top-users-days, results = "hide", eval = Sys.Date() >= start_date}
plot_list <- lapply(seq_along(days), function(idx) {
    tweets_days %>%
        filter(date == days[idx]) %>%
        group_by(screen_name, is_retweet) %>%
        summarise(count = n()) %>%
        group_by(screen_name) %>%
        mutate(total = sum(count)) %>%
        ungroup() %>%
        arrange(desc(total)) %>%
        slice(1:20) %>% 
        ggplot(aes(reorder(screen_name, total), count, fill = !is_retweet)) +
            geom_col() +
            scale_fill_tweet_type +
            coord_flip() + 
            labs(x = "Screen Name", y = "Tweets",
                 title = paste(hashtags_query, "tweets by user, Day", idx),
                 subtitle = "top 20 users")
})

src_list <- lapply(seq_along(plot_list), function(idx) {
    src <- c("#### Day <<idx>> {.unnumbered}",
             "```{r tweets-top-users-day<<idx>>}",
             "plot_list[[<<idx>>]]",
             "```",
             "")
    knit_expand(text = src, delim = c("<<", ">>"))
})

out <- knit_child(text = unlist(src_list))
```

`r if (Sys.Date() >= start_date) out`

### Original {.unnumbered .tabset .tabset-fade}

```{r tweets-top-users-orig-days, results = "hide", eval = Sys.Date() >= start_date}
plot_list <- lapply(seq_along(days), function(idx) {
    tweets_days %>% 
        filter(date == days[idx]) %>%
        ungroup() %>%
        filter(is_retweet == FALSE) %>%
        count(screen_name) %>% 
        arrange(desc(n)) %>%
        slice(1:20) %>% 
        ggplot(aes(reorder(screen_name, n), n)) +
            geom_col(fill = params$accent) +
            coord_flip() +
            labs(x = "Screen Name", y = "Tweets",
                 title = paste(hashtags_query, "tweets by user, Day", idx),
                 subtitle = "top 20 users (original)")
})

src_list <- lapply(seq_along(plot_list), function(idx) {
    src <- c("#### Day <<idx>> {.unnumbered}",
             "```{r tweets-top-users-orig-day<<idx>>}",
             "plot_list[[<<idx>>]]",
             "```",
             "")
    knit_expand(text = src, delim = c("<<", ">>"))
})

out <- knit_child(text = unlist(src_list))
```

`r if (Sys.Date() >= start_date) out`

### Retweets {.unnumbered .tabset .tabset-fade}

```{r tweets-top-users-retweets-days, results = "hide", eval = Sys.Date() >= start_date}
plot_list <- lapply(seq_along(days), function(idx) {
    tweets_days %>% 
        filter(date == days[idx]) %>%
        ungroup() %>%
        filter(is_retweet == TRUE) %>%
        count(screen_name) %>% 
        arrange(desc(n)) %>%
        slice(1:20) %>% 
        ggplot(aes(reorder(screen_name, n), n)) +
            geom_col(fill = params$accent2) +
            coord_flip() +
            labs(x = "Screen Name", y = "Tweets",
                 title = paste(hashtags_query, "tweets by user, Day", idx),
                 subtitle = "top 20 users (retweets)")
})

src_list <- lapply(seq_along(plot_list), function(idx) {
    src <- c("#### Day <<idx>> {.unnumbered}",
             "```{r tweets-top-users-retweets-day<<idx>>}",
             "plot_list[[<<idx>>]]",
             "```",
             "")
    knit_expand(text = src, delim = c("<<", ">>"))
})

out <- knit_child(text = unlist(src_list))
```

`r if (Sys.Date() >= start_date) out`

# Sources {.tabset .tabset-pills}

## Users {.unnumbered}

```{r tweets-top-sources-users}
tweets %>% 
    distinct(screen_name, source) %>%
    count(source) %>% 
    filter(n >= 5) %>% 
    ggplot(aes(reorder(source, n), n)) +
        geom_col(fill = params$accent) +
        coord_flip() + 
        labs(x = "Source", y = "Users",
             title = paste(hashtags_query, "users by source"),
             subtitle = "sources with at least 5 distinct users")
```

## Tweets {.unnumbered}

```{r tweets-top-sources}
tweets %>% 
    count(source, is_retweet) %>%
    group_by(source) %>%
    mutate(total_n = sum(n)) %>%
    ungroup() %>%
    filter(total_n >= 5) %>% 
    ggplot(aes(reorder(source, total_n), n, fill = !is_retweet)) +
        geom_col() +
        coord_flip() +
        scale_fill_tweet_type +
        labs(x = "Source", y = "Tweets",
             title = paste(hashtags_query, "tweets by source"),
             subtitle = "sources with at least 5 tweets")
```

# Networks

## Replies

The "replies network", composed from users who reply directly to one another, 
coloured by PageRank.

```{r reply-network, eval = sum(!is.na(tweets$reply_to_screen_name)) > 5}
tweets_replies <- tweets %>% 
    filter(!is.na(reply_to_screen_name)) %>% 
    select(screen_name, reply_to_screen_name) %>% 
    graph.data.frame(directed = TRUE)

V(tweets_replies)$label <- V(tweets_replies)$name
V(tweets_replies)$id    <- V(tweets_replies)$name
V(tweets_replies)$pr    <- page_rank(tweets_replies)$vector

ggraph(tweets_replies, layout = "fr") +
    geom_edge_link(arrow = arrow(length = unit(4, 'mm')), 
                   end_cap = circle(1, 'mm'),
                   colour = "darkgrey") +
    geom_node_point(aes(colour = pr)) +
    geom_node_text(aes(label = label), colour = params$accent, repel = FALSE) +
    scale_colour_viridis_c() +
    theme_graph() +
    theme(legend.position = "none")
```

## Mentions

The "mentions network", where users mention other users in their tweets.
Filtered for a k-core of `r params$kcore`. Node colour and size adjusted
according to  PageRank score.

```{r mentions-network}
tweets_mentions <- tweets %>% 
    filter(!is.na(mentions_screen_name)) %>% 
    select(screen_name, mentions_screen_name) %>% 
    unnest(mentions_screen_name) %>% 
    mutate(mentions_screen_name = strsplit(mentions_screen_name, " ")) %>% 
    unnest(mentions_screen_name) %>% 
    graph.data.frame()

V(tweets_mentions)$label <- V(tweets_mentions)$name
V(tweets_mentions)$id    <- V(tweets_mentions)$name
V(tweets_mentions)$pr    <- page_rank(tweets_mentions)$vector
V(tweets_mentions)$kcore <- coreness(tweets_mentions)
lo_kcore <- V(tweets_mentions)$kcore < params$kcore
tweets_mentions <- delete_vertices(tweets_mentions,
                                   V(tweets_mentions)[lo_kcore])

ggraph(tweets_mentions, layout = "fr") +
    geom_edge_link(arrow = arrow(length = unit(2, 'mm')), 
                   end_cap = circle(1, 'mm'),
                   width = 0.1, colour = "darkgrey") +
    geom_node_point(aes(colour = pr)) +
    geom_node_text(aes(label = label, size = pr,),
                   colour = params$accent, repel = FALSE) +
    scale_colour_viridis_c() +
    theme_graph() +
    theme(legend.position = "none")
```

# Tweet types

## Retweets {.tabset .tabset-pills}

### Proportion {.unnumbered}

```{r is-retweet}
tweets %>% 
    count(is_retweet) %>% 
    ggplot(aes(is_retweet, n, fill = !is_retweet)) +
    geom_col() +
        scale_fill_tweet_type +
        labs(x = "Is retweet", y = "Tweets",
             title = paste(hashtags_query, "tweets by retweet status"))
```

### Count {.unnumbered}

```{r retweet-count}
tweets %>% 
    ggplot(aes(retweet_count)) +
        geom_histogram(bins = max(tweets$retweet_count), fill = params$accent) +
        labs(x = "Retweet count", y = "Tweets",
             title = paste(hashtags_query,
                           "distribution of retweets per tweet"))
```

### Top 10 {.unnumbered}

```{r top-retweeted}
top <- tweets %>% 
    filter(is.na(retweet_status_id)) %>%
    filter(retweet_count > 0) %>%
    select(status_id, screen_name, text, retweet_count) %>%
    arrange(desc(retweet_count)) %>% 
    distinct() %>%
    slice(1:10)

top %>%
    select(-status_id) %>% 
    kable(format = "html")
```

### Most retweeted {.unnumbered}

```{r most-retweeted}
tryCatch({
    tweet_shot(top$status_id[1])
}, error = function(msg) {
    if (grepl("Twitter status not found", msg)) {
        "Tweet not found, it may have been deleted "
    } else {
        stop(msg)
    }
})
```

## Likes {.tabset .tabset-pills}

### Proportion {.unnumbered}

```{r has-favorite}
tweets %>% 
    mutate(has_favorite = ifelse(favorite_count > 0, TRUE, FALSE)) %>% 
    count(has_favorite, is_retweet) %>%
    ggplot(aes(has_favorite, n, fill = !is_retweet)) +
        geom_col() + 
        scale_fill_tweet_type +
        labs(x = "Has like", y = "Tweets",
             title = paste(hashtags_query, "tweets by liked status"))
```

### Count {.unnumbered}

```{r favorite-count}
tweets %>% 
    ggplot(aes(favorite_count)) +
        geom_histogram(bins = max(tweets$favorite_count),
                       fill = params$accent) +
        labs(x = "Like count", y = "Tweets",
             title = paste(hashtags_query,
                           "distribution of likes per tweet"))
```

### Top 10 {.unnumbered}

```{r top-favorited}
top <- tweets %>% 
    filter(favorite_count > 0) %>%
    select(status_id, screen_name, text, favorite_count) %>%
    arrange(desc(favorite_count)) %>% 
    distinct() %>%
    slice(1:10)

top %>%
    select(-status_id) %>% 
    kable(format = "html")
```

### Most likes {.unnumbered}

```{r most-favorited}
tryCatch({
    tweet_shot(top$status_id[1])
}, error = function(msg) {
    if (grepl("Twitter status not found", msg)) {
        "Tweet not found, it may have been deleted "
    } else {
        stop(msg)
    }
})
```

## Quotes {.tabset .tabset-pills}

### Proportion {.unnumbered}

```{r is-quote}
tweets %>% 
    count(is_quote, is_retweet) %>% 
    ggplot(aes(is_quote, n, fill = is_retweet)) +
        geom_col() +
        scale_fill_tweet_type +
        labs(x = "Is quote", y = "Tweets",
             title = paste(hashtags_query, "tweets by quote status"))
```

### Count {.unnumbered}

```{r quotes-count}
tweets %>% 
    filter(!is.na(quoted_status_id)) %>% 
    count(quoted_status_id) %>% 
    ggplot(aes(n)) +
        geom_histogram(bins = 10, fill = params$accent) +
        labs(x = "Quote count", y = "Tweets",
             title = paste(hashtags_query,
                           "distribution of quotes per tweet")) + 
        scale_x_continuous(limits = c(0, 10), breaks = seq(0, 10, 2))
```

### Top 10 {.unnumbered}

```{r top-quoted}
top <- tweets %>% 
    filter(!is.na(quoted_status_id)) %>% 
    count(quoted_status_id) %>% 
    filter(n > 0) %>% 
    arrange(desc(n)) %>% 
    inner_join(select(tweets, status_id, screen_name, quoted_status_id,
                      is_retweet, text), by = "quoted_status_id") %>% 
    filter(is_retweet == FALSE) %>% 
    select(status_id, screen_name, text, quote_count = n) %>%
    distinct() %>%
    slice(1:10)
  
top %>%
    select(-status_id) %>%
    kable(format = "html")
```

### Most quoted {.unnumbered}

```{r most-quoted}
tryCatch({
    tweet_shot(top$status_id[1])
}, error = function(msg) {
    if (grepl("Twitter status not found", msg)) {
        "Tweet not found, it may have been deleted "
    } else {
        stop(msg)
    }
})
```

# Media {.tabset .tabset-pills}

## Proportion {.unnumbered}

```{r has-media}
tweets %>% 
    mutate(has_media = !is.na(media_url)) %>%
    count(has_media, is_retweet) %>% 
    ggplot(aes(has_media, n, fill = !is_retweet)) +
        geom_col() +
        scale_fill_tweet_type +
        labs(x = "Has media", y = "Tweets",
             title = paste(hashtags_query, "tweets by media status"))
```

## Top 10 {.unnumbered}

```{r liked-media}
tweets_media <- tweets %>% 
    filter(!is.na(media_url)) %>% 
    arrange(desc(favorite_count)) %>%
    filter(favorite_count > 0)

tweets_media %>%
    slice(1:10) %>% 
    select(screen_name, text, favorite_count) %>%
    kable(format = "html")
```

# {.unnumbered .toc-ignore}

## Most liked image

![](`r tweets_media[1, "media_url"]`)

# Tweet text

## Word cloud

The top 100 words used 3 or more times.

```{r count-words}
data("stop_words")

tweets %>% 
    filter(is_retweet == FALSE) %>% 
    unnest_tokens(word, text) %>% 
    select(word) %>% 
    filter(!word %in% c(gsub("#", "", tolower(hashtags_vec)),
                        "https", "t.co", "amp"),
           !word %in% tolower(tweets$screen_name), 
           !grepl("^\\d+$", word)) %>% 
    anti_join(stop_words, by = "word") %>%
    count(word) %>% 
    with(wordcloud(word, n, max.words = 100, min.freq = 3,
                 colors = brewer.pal(6, "Spectral")))
```

## Hashtags

Other hashtags used 5 or more times.

```{r hashtags}
tweets %>% 
    filter(is_retweet == FALSE) %>%
    select(text) %>%
    mutate(text = str_split(text, "[:space:]")) %>%
    unnest(text) %>%
    filter(str_detect(text, "^#")) %>%
    mutate(
        text = str_remove_all(text, "[:punct:]"),
        text = str_to_lower(text),
        text = stringi::stri_trans_general(text, "latin-ascii")
    ) %>%
    count(text) %>%
    filter(
        !(text %in% str_remove(tolower(hashtags_vec), "#")),
        n >= 5
    ) %>%
    slice_max(n, n = 30) %>%
    ggplot(aes(reorder(text, n), n)) +
        geom_col(fill = params$accent) +
        coord_flip() +
        labs(x = "Hashtag", y = "Tweets",
             title = paste("Other hashtags used with", hashtags_query),
             subtitle = paste("30 most common alternative hashtags used at",
                              "least 5 times in original tweets"))
```

## Bigram graph

Words that were tweeted next to each other at least `r params$bigram_filter`
times.

```{r bigram-graph}
tweets %>% 
    filter(is_retweet == FALSE) %>%
    select(text) %>%
    unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
    separate(bigram, c("word1", "word2"), sep = " ") %>%
    filter(!word1 %in% stop_words$word,
           !word1 %in% c(gsub("#", "", tolower(hashtags_vec)),
                         "https", "t.co", "amp"),
           !word1 %in% tolower(tweets$screen_name), 
           !grepl("^\\d+$", word1)) %>%
    filter(!word2 %in% stop_words$word,
           !word2 %in% c(gsub("#", "", tolower(hashtags_vec)),
                         "https", "t.co", "amp"),
           !word2 %in% tolower(tweets$screen_name), 
           !grepl("^\\d+$", word2)) %>%
    count(word1, word2, sort = TRUE) %>%
    filter(n >= params$bigram_filter) %>%
    graph_from_data_frame() %>%
    ggraph(layout = "fr") +
        geom_edge_link(aes(edge_colour = n),
                       arrow = arrow(type = "closed",
                                     length = unit(2, 'mm')),
                       end_cap = circle(1, 'mm')) +
        geom_node_point(size = 2, colour = params$accent) +
        geom_node_text(aes(label = name), vjust = 1, hjust = 0.5,
                       repel = TRUE, segment.colour = "pink") +
        scale_edge_color_gradientn(colours = viridis(100)) +
        theme_graph()
```

## Topic modelling

Top 10 words associated with `r params$topics_k` topics identified by LDA.

```{r topic-modelling}
topics <- tweets %>% 
    filter(is_retweet == FALSE) %>%
    select(document = status_id, text) %>%
    unnest_tokens(word, text) %>%
    filter(!word %in% stop_words$word,
           !word %in% c(gsub("#", "", tolower(hashtags_vec)),
                        "https", "t.co", "amp"),
           !word %in% tolower(tweets$screen_name), 
           !grepl("^\\d+$", word)) %>%
    count(document, word, sort = TRUE) %>%
    ungroup() %>%
    cast_dtm(document, word, n) %>%
    LDA(k = params$topics_k, control = list(seed = 1))
```

```{r topics-words}
topics %>%
    tidy(matrix = "beta") %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    arrange(topic, -beta) %>%
    mutate(term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(x = term, y = beta, fill = factor(topic))) +
        geom_col(show.legend = FALSE, fill = params$accent) +
        scale_x_reordered() +
        facet_wrap(~ topic, scales = "free") +
        coord_flip() +
        labs(y = "beta (occurence in topics)",
             title = "Topic modelling",
             subtitle = paste("Top terms for", params$topics_k,
                              "LDA topics associated with", hashtags_query)) + 
        theme(axis.title.y = element_blank())
```

### Representative tweets {.tabset .tabset-fade}

Most representative tweets for each topic

```{r topics-tweets, results = "hide"}
topics_list <- topics %>%
    tidy(matrix = "gamma") %>%
    group_by(document) %>%
    top_n(1, gamma) %>%
    ungroup() %>%
    group_by(topic) %>%
    top_n(10, gamma) %>%
    arrange(-gamma) %>%
    left_join(tweets, by = c(document = "status_id")) %>%
    select(topic, screen_name, text, gamma) %>%
    split(.$topic)
    
src_list <- lapply(seq_along(topics_list), function(idx) {
    src <- c("#### Topic <<idx>> {.unnumbered}",
             "```{r topics-tweets-topic<<idx>>}",
             "kable(topics_list[[<<idx>>]][, -1], format = 'html')",
             "```",
             "")
    knit_expand(text = src, delim = c("<<", ">>"))
})

out <- knit_child(text = unlist(src_list))
```

`r out`

# Links

Links to GitHub, GitLab, BitBucket, Bioconductor or CRAN mentioned in Tweets.

```{r links}
url_counts <- tweets %>%
    unnest(urls_expanded_url) %>%
    group_by(urls_expanded_url) %>%
    summarise(
        Tweets   = sum(!is_retweet),
        Retweets = sum(is_retweet),
        .groups = "drop"
    ) %>%
    mutate(Total = Tweets + Retweets)

urls <- tweets %>%
    pull(urls_expanded_url) %>%
    discard(~ all(is.na(.x))) %>%
    flatten_chr() %>%
    unique()

regexes <- list(
    c(Type = "GitHub",
      re = "http[s]?://github.com/[\\w-]+/([A-Za-z0-9_\\.-]+).*"),
    c(Type = "GitLab",
      re = "http[s]?://gitlab.com/[\\w-]+/([A-Za-z0-9_\\.-]+).*"),
    c(Type = "BitBucket",
      re = "http[s]?://bitbucket.org/[\\w-]+/([A-Za-z0-9_\\.-]+).*"),
    c(Type = "Bioc",
      re = "https://bioconductor.org/packages.*/([A-Za-z0-9_\\.-]+).*"),
    c(Type = "CRAN",
      re = "https://cran.*/packages/([A-Za-z0-9_\\.-]+).*")
)

software <- map_df(regexes, function(re) {
    urls %>%
        str_match(re["re"]) %>%
        as_tibble(.name_repair = "unique") %>%
        rename(URL = "...1", Name = "...2") %>%
        mutate(Type = re["Type"])
}) %>%
    drop_na() %>%
    mutate(
        LinkURL = case_when(
            Type == "GitHub" ~ str_to_lower(str_replace(URL, "http:", "https:")),
            Type == "GitLab" ~ str_to_lower(str_replace(URL, "http:", "https:")),
            Type == "BitBucket" ~ str_to_lower(str_replace(URL, "http:", "https:")),
            Type == "Bioc" ~ paste0("https://bioconductor.org/packages/", Name),
            Type == "CRAN" ~ paste0("https://CRAN.R-project.org/package=", Name),
            TRUE ~ URL
        )
    ) %>%
    mutate(
        Link = str_remove(LinkURL, "https://"),
        Link = str_remove(Link, "github.com/"),
        Link = str_remove(Link, "gitlab.com/"),
        Link = str_remove(Link, "bitbucket.org/"),
        Link = paste0("[", str_trunc(Link, 70), "](", LinkURL, ")")
    ) %>% 
    left_join(url_counts, by = c(URL = "urls_expanded_url")) %>%
    arrange(desc(Total), desc(Tweets), desc(Retweets), Name) %>%
    select(Name, Tweets, Retweets, Type, Link)
```

`r if (nrow(software) >= 1) kable(software)`
